\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
recompile

While for \ClaudeThreeFiveSonnet the overall performance did not change, we observe a decrease in performance for \GPTFourO compared with the \llm without tools (\Cref{tab:performance_table}). 
If we study the results by each type of question, we observe an improvement for questions regarding electron counts or point groups of compounds.
However, the scores decreased for questions asking about the number of isomers or \gls{ghs} pictograms.
For the specific questions about converting \gls{iupac} names to \gls{smiles}, the results decreased notably despite the models having access to specific tools prepared for those questions. 
By studying the reasoning path for these cases, we found that the error results from the models responding in a format that the LangChain framework with the default ReAct loop cannot handle. 
This indicates that agent frameworks need optimization to be more robust. It involves not only equipping the \glspl{llm} with tools but also necessitates engineering efforts to create robust systems.

>>>>

While for \ClaudeThreeFiveSonnet the overall performance did not change, we observe a decrease in performance for \GPTFourO compared with the \gls{llm} without tools (\Cref{tab:performance_table}).
If we study the results by each type of question, we observe an improvement for questions regarding electron counts or point groups of compounds.
However, the scores decreased for questions asking about the number of isomers or \gls{ghs} pictograms.
For the specific questions about converting \gls{iupac} names to \gls{smiles}, the results decreased notably despite the models having access to specific tools prepared for those questions.
By studying the reasoning path for these cases, we found that the error results from the models responding in a format that the LangChain framework with the default ReAct loop cannot handle.
This indicates that agent frameworks need optimization to be more robust. It involves not only equipping the \glspl{llm} with tools but also necessitates engineering efforts to create robust systems.
